A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-07-17 07_Manuscript.Rmd
Correct references and remove redundant code

# Data
PM_Mdat <- read.csv(here("cache/PM_MB_updated.csv"))
load(file = here("cache/Meta-analysisData.Rdata"))
load(file = here("cache/PreliminaryData.Rdata"))
PM_MB_dat%>% 
   filter(fungicide_ai == "tebuconazole")
```

@@

Mungbean was first brought to Australia in the 1930s for use as a forage or green manure crop and it was only as recent as the 1960s until that mungbean was grown commercially [@aboutAMA, @Chuahan2018].
At the end of the 1980s between 3 - 10 thousand hectares were being harvested for dried beans, of which mungbean is categorised by the FAO statistics data repository [@FAOSTAT].
In the decade leading up to 2018 between 35 - 86.4 thousand hectares of dried beans were planted annually. 
This increase is attributed high value export markets and to the improved yields in the new cultivars [@Clarry2016].
Currently mungbean is predominantly grown in southern Queensland and northern New South Wales as a short season summer legume crop.
In 2019, approximately 90&nbsp;% of Australian mungbean was grown for export with lucrative returns of up to \$1300&nbsp;AU a tonne [@QueenslandGovernment2019].
Mungbean potentially yields up to 3 tonnes per hectare [@ThomasRobert2004], but due to high variability in yields between seasons and locations, the average Australian farm still yields less than 1 tonne per hectare [@Chauhan2018].

>>>>

# Data
PM_Mdat <- read.csv(here("cache/PM_MB_updated.csv"))
load(file = here("cache/Meta-analysisData.Rdata"))
load(file = here("cache/PreliminaryData.Rdata"))
```

@@

Mungbean was first brought to Australia in the 1930s for use as a forage or green manure crop and it was only as recent as the 1960s until that mungbean was grown commercially [@aboutAMA, @Chauhan2018].
At the end of the 1980s between 3 - 10 thousand hectares were being harvested for dried beans, of which mungbean is categorised by the FAO statistics data repository [@FAOSTAT].
In the decade leading up to 2018 between 35 - 86.4 thousand hectares of dried beans were planted annually. 
This increase is attributed high value export markets and to the improved yields in the new cultivars [@Clarry2016].
Currently mungbean is predominantly grown in southern Queensland and northern New South Wales as a short season summer legume crop.
In 2019, approximately 90&nbsp;% of Australian mungbean was grown for export with lucrative returns of up to \$1300&nbsp;AU a tonne [@QueenslandGovernment2019].
Mungbean potentially yields up to 3 tonnes per hectare [@ThomasRobert2004], but due to high variability in yields between seasons and locations, the average Australian farm still yields less than 1 tonne per hectare [@Chauhan2018].
